GMSE: an R package for generalised management strategy evaluation

### 2017-11-16 notebook/ms/SI1.Rmd
Fix Pozo name
Add Saro's suggestion to redefine 'individual' in manager fitness section

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie, Jeremy J. Cusack, Isabel L. Jones, Erlend B. Nilsen, Roc&#0237;o
  Pozo, O. Sarobidy Rakotonarivo, Bram Van Moorter, and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
subtitle: Supporting Information 1
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

Individual fitness as calculated for managers ($F_{i}^{m}$) is affected by a manager's utility for resources and the projected change in resource abundance caused by the individual's policy (i.e., the contents of their `POPULATION` layer, specifically row 3). Manager utility for a resource ($U^{m}_{res}$) is defined as the difference between `manage_target` and the estimation of population abundance as produced by the GMSE observation model (see "[Key data structures used](#Key_data_structures_used)" above). Manager utility can therefore change in each GMSE time step as estimated resource abundance changes; when the estimated resource abundance is greater than `manage_target`, $U^{m}_{res}$ is negative, and when the estimated resource abundance is less than `manage_target`, $U^{m}_{res}$ is positive. To get individual fitness, first the change in resource abundance predicted by the individual's policy ($\Delta A_{i}$) is calculated, then the squared difference between $\Delta A_{i}$ and $U^{m}_{res}$ is calculated to obtain a utility deviation ($D_{i}$) for the individual $i$,

>>>>

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie, Jeremy J. Cusack, Isabel L. Jones, Erlend B. Nilsen, Roc&#0237;o
  A. Pozo, O. Sarobidy Rakotonarivo, Bram Van Moorter, and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
subtitle: Supporting Information 1
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

Individual fitness as calculated for managers ($F_{i}^{m}$) is affected by a manager's utility for resources and the projected change in resource abundance caused by the individual's policy (i.e., the contents of their `POPULATION` layer, specifically row 3; here again we use 'individual' to refer to one of `ga_popsize` discrete strategies in `POPULATION`, which may be selected and reproduce within the genetic algorithm). Manager utility for a resource ($U^{m}_{res}$) is defined as the difference between `manage_target` and the estimation of population abundance as produced by the GMSE observation model (see "[Key data structures used](#Key_data_structures_used)" above). Manager utility can therefore change in each GMSE time step as estimated resource abundance changes; when the estimated resource abundance is greater than `manage_target`, $U^{m}_{res}$ is negative, and when the estimated resource abundance is less than `manage_target`, $U^{m}_{res}$ is positive. To get the fitness of individuals, first the change in resource abundance predicted by the individual's policy ($\Delta A_{i}$) is calculated, then the squared difference between $\Delta A_{i}$ and $U^{m}_{res}$ is calculated to obtain a utility deviation ($D_{i}$) for the individual $i$,
